---
title: "p8105_hw6_hc3212"
author: "Hening CUi"
date: "12/1/2021"
output: github_document
---

```{r,echo = FALSE}
library (tidyverse)
library(viridis)
library(modelr)
library(mgcv)
library(MASS)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

knitr::opts_chunk$set(
  fig.width = 8,
  fig.height =6,
  out.width = "90%",
  message = FALSE,
  warning = FALSE,
  error = FALSE
)

options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

First import and clean the data.

```{r}
baby_df = 
  read_csv("birthweight.csv") %>% 
  drop_na() %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    mrace = as.factor(mrace),
  ) %>% 
  dplyr::select(-pnumlbw, -pnumsga)
```

I use the backwards elimination to creat the optimal linear regression. Firstly, all the predictor was included to generate the linear regression. Then the less significant predictor was removed, which p-value less than SL(0.05). The final model contains babysex, bhead, blength, delwt, fincome,  
gaweeks, mheight, mrace, parity, ppwt and smoken.

```{r}
mult.fit = lm(bwt ~ ., data = baby_df)
summary(mult.fit)

final.model <- stepAIC(mult.fit, direction = "both", trace = FALSE) 
summary(final.model)
```


```{r}
baby_df%>% 
  add_predictions(final.model) %>% 
  add_residuals(final.model) %>% 
  ggplot(aes(x = pred, y = resid, alpha = 0.1)) +
  geom_point()
```

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

Compare models

First, sampling...

```{r}
baby_cv =
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

Next, Fit models


```{r, eval=FALSE}
fit_function = function(df, obser){

  multi_model = mult.fit = lm(obser ~ ., data = df)
  
  final.model <- stepAIC(mult_model, direction = "both", trace = FALSE)
  
  return(final.model)
}
```

```{r, eval=FALSE}
fit_df =
  baby_cv %>% 
  mutate(
    final_mod = map2(.x = train, .y = bwt, ~ fit_function(df = .x, obser = .y)),
    len_mod = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    hea_mod = map(.x = train, ~lm(bwt ~ bhead + blength + babysex, data = .x))
  ) %>% 
  mutate(
    rmsefinal = map2_dbl(.x = final_mod,.y = test, ~rmse(model = .x, data = .y)),
    rmselen = map2_dbl(.x = len_mod,.y = test, ~rmse(model = .x, data = .y)),
    rmsehea = map2_dbl(.x = hea_mod,.y = test, ~rmse(model = .x, data = .y))
  )

```

```{r, eval=FALSE}
fit_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    rmsefinal:rmsehea,
    names_to = "model",
    values_to = "rmse", 
    names_prefix = "rmse"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```

## Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  dplyr::select(name, id, everything())
```




